\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-11-18 doc/USER_MANUAL/manual_SPECFEM3D.tex
fixed the references in the new chapter about inversions

Whatever misfit function you use for the tomographic inversion \citep[several examples in][]{TrTaLi05}, you will weight the sensitivity kernels with measurements. Furthermore, you will use as many measurements (stations, components, time windows) as possible per event; hence, we call these composite kernels ``event kernels,'' which are volumetric fields representing the gradient of the misfit function with respect to one of the variables (\eg $V_{\rm s}$). The basic features of an adjoint-based tomographic inversion were illustrated in \citet{TaLiTr07} using a conjugate-gradient algorithm; there are dozens of versions of gradient-based inversion algorithms that could alternatively be used. The tomographic inversion of \citet{TaLiMaTr09,TaLiMaTr2010} used SPECFEM3D as well as several additional components which are also stored on the CIG svn server, described next.

>>>>

Whatever misfit function you use for the tomographic inversion (several examples in \cite{TrTaLi05} and \cite{TrKoLi08}), you will weight the sensitivity kernels with measurements. Furthermore, you will use as many measurements (stations, components, time windows) as possible per event; hence, we call these composite kernels ``event kernels,'' which are volumetric fields representing the gradient of the misfit function with respect to one of the variables (\eg $V_{\rm s}$). The basic features of an adjoint-based tomographic inversion were illustrated in \citet{TaLiTr07} and \citet{TrKoLi08} using a conjugate-gradient algorithm; there are dozens of versions of gradient-based inversion algorithms that could alternatively be used. The tomographic inversion of \citet{TaLiMaTr09,TaLiMaTr2010} used SPECFEM3D as well as several additional components which are also stored on the CIG svn server, described next.
